---
title: "Data Cleaning"
author: "Yuxuan Li"
date: "8/28/2019"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(zoo)
library(lubridate)
library(ggplot2)
library(stringr)

# packages for word cloud
# install.packages("tm")  # for text mining
# install.packages("SnowballC") # for text stemming
# install.packages("wordcloud") # word-cloud generator 
# install.packages("RColorBrewer") # color palettes
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")

# read airbnb.data from csv file
bnb.raw <- read.csv("airbnb_data.csv") 
```

# processing data and save to "bnb_data.Rdata"
* date (as data, date length between host_since and first review)
* ammenity (described later(maybe))
* NA's (described later)
* zipcode (add 0 to beginning)
* host_response_rate: percentage to digits
* qualitative vars:
  + room_type (Entire house/apt) -> is_Entire
  + room_type (Entire/Private) -> is_Private
  + bed_type -> is_RealBed 
  + Cancellation policy (if somewhat strict) -> is_CancelStrict
  
## NA's 
8333 obs have NA's. In the dataset, 2 types of NA's are observed: random and systematical.
* Random NA's are rare, randomly happened, including
  + bathrooms 95
  + bedrooms 41
  + beds 59
  + host_has_profile_pic 91
  + host_identity_verified 91
  + host_since 91
  
* Systematical NA's are typically because of no review, including:
  + first_review: 7717
  + last_review: 7696
  + review_scores_rating: 8143

We simply dropped random NA's. For systimetical one's, we assign sample mean to review_scores_rating, and sample max to post_wait, which is the day-difference between host_since and first_review. Then remove first_review and last_review. 
  
## amenities

Hosts list their amenities. 

```{r readdata}
# deal with date and zipcode
bnb.data <- bnb.raw %>% # date
  mutate(host_since   = as.Date(host_since,   format = "%m/%d/%y"),
         first_review = as.Date(first_review, format = "%m/%d/%y"),
         last_review  = as.Date(last_review,  format = "%m/%d/%y")) %>%
  mutate(post_wait = time_length(host_since %--% first_review, unit = "day")) %>%
  mutate(zipcode = as.character(zipcode)) %>% # zipcode
  mutate(zipcode = str_pad(zipcode,5,side="left",pad="0"))

# deal with '%'
bnb.data <- bnb.data %>%
  mutate(host_response_rate = as.character(host_response_rate),
         host_response_rate = str_sub(host_response_rate,1L,-2L), #remove "%"
         host_response_rate = as.numeric(host_response_rate)*0.01) # trans to digit

# Deal with NA's
  # systematical
  score_mean <- mean(na.omit(bnb.data$review_scores_rating))
  response_mean <- mean(na.omit(bnb.data$host_response_rate))
  wait_max <- max(na.omit(bnb.data$post_wait))
  bnb.data <- bnb.data %>%
    mutate(review_scores_rating = ifelse(is.na(review_scores_rating)==TRUE,score_mean,
                                         review_scores_rating),
           host_response_rate = ifelse(is.na(host_response_rate)==TRUE, response_mean,
                                       host_response_rate),
           post_wait = ifelse(is.na(post_wait)==TRUE,wait_max,post_wait)) %>%
    dplyr::select(-first_review, -last_review)
  # ramdom
  bnb.data <- na.omit(bnb.data)

# deal with amenities
bnb.data <- bnb.data %>%
  mutate(amenities = as.character(amenities)) %>%
  mutate(number_of_amenities = 1 + str_count(amenities, ",")) %>%
  mutate(am_Internet = (str_detect(amenities, "Internet") | 
           str_detect(amenities, "Wireless Internet")),
         am_TV = (str_detect(amenities, "TV") | str_detect(amenities, "Cable TV")),
         am_AC = str_detect(amenities, "Air conditioning"),
         am_Kitchen = str_detect(amenities, "Kitchen"),
         am_Heating = str_detect(amenities, "Heating"),
         am_Washer = str_detect(amenities, "Washer"),
         am_Dryer = str_detect(amenities, "Dryer"),
         am_Parking = str_detect(amenities, "Free parking on premises"),
         am_Shampoo = str_detect(amenities, "Shampoo"),
         am_Smoke = str_detect(amenities, "Smoke detector"),
         am_Hangers = str_detect(amenities, "Hangers"),
         am_Iron = str_detect(amenities, "Iron"),
         am_Fire = str_detect(amenities, "Fire extinguisher"),
         am_Firstaid = str_detect(amenities, "First aid kit"))

# add has_review for those has review
bnb.data <- bnb.data %>%
  mutate(has_review = ifelse(number_of_reviews==0,0,1),
         has_review = as.factor(has_review))

# Deal with qualitative data
bnb.data <- bnb.data %>%
  mutate(is_Entire = ifelse(room_type == "Entire home/apt", 1,0),
         is_Private = ifelse(room_type != "Shared room", 1,0),
         is_RealBed = ifelse(bed_type == "Real Bed",1,0),
         is_CancelStrict = ifelse((cancellation_policy == "moderate" | 
                                    cancellation_policy == "flexible"),0,1)) %>%
  mutate(cleanning_fee = ifelse(cleaning_fee == FALSE,0,1),
         host_has_profile_pic = ifelse(host_has_profile_pic=="f",0,ifelse(host_has_profile_pic == "t",1, NA)),
         host_identity_verified = ifelse(host_identity_verified == "f",0,ifelse(host_identity_verified=="t",1,host_identity_verified)),
         instant_bookable = ifelse(instant_bookable=="t",1,0))


# remove outlier (the one with log-price == 0)
bnb.data <- filter(bnb.data, log_price != 0)


# split training and testing
set.seed(1)
train <- sample(nrow(bnb.data), 0.75*nrow(bnb.data))
train.data <- bnb.data[train,]
test.data <- bnb.data[-train,] 

save(bnb.data,train.data,test.data, file = "bnb_data.Rdata")

```

```{r amme}
# http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know 

# find Top10 listed amenities
ame <- str_c(bnb.data$amenities, sep = "", collapse = "") %>%
       str_to_title() %>%
       str_replace_all(" ", "") %>%
       str_replace_all("\\{", "") %>%
       str_replace_all("\\}", "") %>%
       str_replace_all(",", " ")
# Load the data as a corpus
docs <- Corpus(VectorSource(ame))

# text transformation
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "\"")


# Build a term-document matrix
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)

write.table(d, file = "top_listed_amenity.txt", sep = ",", quote = FALSE, row.names = F)

# Word cloud
set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r summ}

summary(bnb.data)

test.data <- bnb.data %>%
  filter(post_wait < 0) #22 obs has host_since > first_review...

test.data <- bnb.data %>%
  filter(number_of_amenities >= 50)
```



```{r data vis}

attach(bnb.data)

ggplot(bnb.data,aes(x=post_wait))+geom_density()
hist(post_wait)
hist(price)
hist(accommodates)
hist(beds)
hist(bedrooms)

```