---
title: "StatDescript"
author: "Yuxuan Li"
date: "9/2/2019"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)

# upload data
load("bnb_data.Rdata")

# upload packages
library(dplyr)
library(ggplot2)
```

```{r summary}
summary(bnb.data)
```

# 1.Number of amenity

First of first, take a look of numeric characters on price, including the numbers of **accomodates, beds, bedrooms, and bathrooms**. Do scatter plot and violin plot of (log-)price on each varaiable. 


### Conclusion:

* The log price and those numbers have roughly positive relationship (sort of sigmoid). I think quadratic term might be necessary in linear regression. 

* Further controls are needed. 


```{r no. amenity}
amen.data <- bnb.data %>%
  select(price, log_price, accommodates, beds, bedrooms, bathrooms) %>%
  na.omit()

summary(amen.data)


# log price to ammenity numbers
par(mfrow = c(2, 2))
for (i in 3:6){
  plot(amen.data[,2] ~ amen.data[,i],
        xlab = colnames(amen.data)[i], ylab = colnames(amen.data)[2])
}

# better(?) version
for (i in 3:6){
  p <- ggplot(amen.data,aes(x = as.factor(amen.data[,i]), y = amen.data[,2])) + 
    geom_violin(scale = "area") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[2])
  
  print(p)
}


# price to ammenity numbers
par(mfrow = c(2, 2))
for (i in 3:6){
plot(amen.data[,1] ~ amen.data[,i],
xlab = colnames(amen.data)[i], ylab = colnames(amen.data)[1])
}

# better(?) version
for (i in 3:6){
  p <- ggplot(amen.data,aes(x = as.factor(amen.data[,i]), y = amen.data[,1])) + 
    geom_violin(scale = "area") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[1])
  
  print(p)
}

```