---
title: "StatDescript"
author: "Yuxuan Li"
date: "9/2/2019"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)

# upload data
load("bnb_data.Rdata")

# upload packages
library(dplyr)
library(ggplot2)
```

```{r summary}
summary(bnb.data)

num.data <- bnb.data
```

# 1.Number of amenity

First of first, take a look of numeric characters on price, including the numbers of **accomodates, beds, bedrooms, and bathrooms**. Do scatter plot and violin plot of (log-)price on each varaiable. 

165 observations removed due to NA's. 

### Conclusion:

* The log price and those numbers have roughly positive relationship (sort of sigmoid). I think quadratic term might be necessary in linear regression. 

* Further controls are needed. 


```{r no. amenity}
amen.data <- bnb.data %>%
  select(price, log_price, accommodates, beds, bedrooms, bathrooms, 
         has_review, number_of_reviews) %>%
  na.omit() # 35835 obs

summary(amen.data)


# log price to ammenity numbers
par(mfrow = c(2, 2))
for (i in 3:6){
  plot(amen.data[,2] ~ amen.data[,i],
        xlab = colnames(amen.data)[i], ylab = colnames(amen.data)[2])
}

# better(?) version
for (i in 3:6){
  p <- ggplot(amen.data,
              aes(x = as.factor(amen.data[,i]), y = amen.data[,2]),
                  fill = has_review) + 
    geom_violin(scale = "width") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[2])
  
  print(p)
}


# price to ammenity numbers
par(mfrow = c(2, 2))
for (i in 3:6){
plot(amen.data[,1] ~ amen.data[,i],
xlab = colnames(amen.data)[i], ylab = colnames(amen.data)[1])
}

# better(?) version
for (i in 3:6){
  p <- ggplot(amen.data,aes(x = as.factor(amen.data[,i]), y = amen.data[,1])) + 
    geom_violin(scale = "width") +
    geom_smooth(aes(x = amen.data[,i], y = amen.data[,1]),method = "lm") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[1])
  
  print(p)
}

```

# 2. Hosts and Reviews

Now consider numerical variables **host_response_rate, number_of_reviews, review_scores_rating**, and logical variables **host_has_profile_pic** and **host_identity_verified**.

Note: if No first_review 
      -> number_of_reviews = 0
      -> review_scores_rating is NA.
      -> No host_response_rate (roughly)

```{r host&review}
hore.data <- bnb.data %>%
  select(price, log_price, 
         host_response_rate, number_of_reviews, review_scores_rating,
         host_has_profile_pic, host_identity_verified) %>%
  mutate(review_scores_rating)
summary(hore.data)


# log price to host and reviews
par(mfrow = c(2, 3))
for (i in 3:7){
  plot(hore.data[,2] ~ hore.data[,i],
        xlab = colnames(hore.data)[i], ylab = colnames(hore.data)[2])
}

# price to host and reviews
par(mfrow = c(2, 3))
for (i in 3:7){
  plot(hore.data[,1] ~ hore.data[,i],
        xlab = colnames(hore.data)[i], ylab = colnames(hore.data)[1])
}

```

# 3. Has Review

**First 5 graphs:**
Group by has_review. No thing interesting...

**Second 5 graphs:**
The price of those have no review get a higher price comparing with those have some reviews. I have that feeling... To verify that thought, plot regression line on plots. And...I'm right.



```{r has review}

summary(bnb.data$has_review)

for (i in 3:6){
  p <- ggplot(amen.data,
              aes(x = as.factor(amen.data[,i]), y = amen.data[,2])) + 
    geom_violin(aes(x = as.factor(amen.data[,i]), y = amen.data[,2],
                    fill = has_review),
                scale = "width") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[2])
  
  print(p)
}


for (i in 3:6){
  p <- ggplot(amen.data,
              aes(x = amen.data[,i], y = amen.data[,2], color = has_review)) + 
    geom_smooth(method = lm) +
    geom_jitter() +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[2])
  
  print(p)
}

# Do the same comparision between review = 0 and review = 1
# this step is no more than extra
zero.data <- filter(amen.data, (number_of_reviews == 0 | number_of_reviews == 1))

for (i in 3:6){
  p <- ggplot(zero.data,
              aes(x = zero.data[,i], y = zero.data[,2], 
                  color = as.factor(number_of_reviews))) + 
    geom_smooth(method = lm) +
    geom_jitter() +
    xlab(colnames(zero.data)[i]) +
    ylab(colnames(zero.data)[2])
  
  print(p)
}
```

# 4. Do something extra

Our prior insights suggests that review_rate should have some relationship, which was not obvious in the scatter plot. So let do some transformation.

Assume price and bedrooms have linear relationship. Plot (log_)price_per_bdrm on rate. This graph, of cource, only apply to those obs with at least one review, and at least one bdrm.

The result suggests that this section is totally redundant. 

```{r price per accom}

# recall the graph in section 1 to see "linear" relationship of price and bdrm
i <- 5
ggplot(amen.data,aes(x = as.factor(amen.data[,i]), y = amen.data[,1])) + 
    geom_violin(scale = "width") +
    geom_smooth(aes(x = amen.data[,i], y = amen.data[,1]),method = "lm") +
    xlab(colnames(amen.data)[i]) +
    ylab(colnames(amen.data)[1])

per.data <- bnb.data %>%
  select(price, bedrooms, review_scores_rating) %>%
  filter(is.na(review_scores_rating)==FALSE & bedrooms>0) %>%
  mutate(price_per_bdrm = price/bedrooms,
         log_price_per_bdrm = log(price_per_bdrm)) 

# Ideally the distribution of price_per_bdrm should be really tight
par(mfrow = c(1, 2))
hist(per.data$price_per_bdrm)
hist(per.data$log_price_per_bdrm)

# do the graph
ggplot(per.data,aes(x = review_scores_rating, y = log_price_per_bdrm)) + 
  geom_point()

ggplot(per.data,aes(x = review_scores_rating, y = price_per_bdrm)) + 
  geom_point()




```

***

# A. Brand new section! Differences across cities.

While all the data come from 6 giant cities, as we already know, Ashley insists that conditions in east and west coast (and midwest) are totally different. So let explore a little bit!

First see general (log-)price distributions across cities. The difference is not quiet big. 

```{r cities}

ggplot(bnb.data, aes(x = city, y = log_price)) +
  geom_boxplot()

# ggplot(bnb.data, aes(x = city, y = price)) +
#   geom_boxplot()
  
```


# B. Price with amenity?

Does AC matter? Does shampoo matter?

```{r amme}
shampoo.data <- bnb.data %>%
  select(log_price, starts_with("am_"))

par(mfrow = c(2, 5))
for (i in 2:11){
  plot(shampoo.data[,1] ~ as.factor(shampoo.data[,i]),
        xlab = colnames(shampoo.data)[i], ylab = colnames(shampoo.data)[1])
}




```